CorReg

### 2015-02-12 www/soutenance.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@1051 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Context}
	\subsection{Industrial context}
		\begin{frame}
				  \begin{enumerate}
				\item Steel industry databases.
				\item Goal: To understand and prevent quality problems on finished product, knowing the whole process, \underline{without a priori}.
			\end{enumerate}
	        \begin{center}
	          \begin{tabular}{ccc}
	         \includegraphics[width=70px,height=70px]{liquid.jpg} & \includegraphics[width=70px,height=70px]{Brame1.jpg} & \includegraphics[width=70px,height=70px]{Brame.jpg} \\
	          	\includegraphics[width=70px,height=70px]{ecras_moy.jpg} & \includegraphics[width=70px,height=70px]{tcc2.jpg} & \includegraphics[width=70px,height=70px]{bobines.jpg}
	          \end{tabular}
	        \end{center}
		\end{frame}
	\subsection{Statistical context}
		\begin{frame}{Regression}
			\begin{equation}
				\boldsymbol{Y}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}\label{regressionsimple}
			\end{equation}
			where 	$\boldsymbol{\varepsilon}\sim \mathcal{N}(0,\sigma_Y^2\boldsymbol{I}_n)$	
		\end{frame}

		\begin{frame}{OLS}
		\begin{figure}[h!]
	\centering
	\includegraphics[width=220px]{figures/OLS_geometric_interpretation.png}
	\caption{Multiple linear regression with Ordinary Least Squares seen as a projection on the $d-$dimensional hyperplane spanned by the regressors $\boldsymbol{X}$. Public domain image.} \label{geomOLS}
	\end{figure}
		\end{frame}

		\begin{frame}{OLS}
		$\boldsymbol{\beta}$ can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{ols}), that is the unbiased maximum likelihood estimator \cite{saporta2006probabilites,dodge2004analyse}: %As shown in section \ref{sectionOLS}, 
	\begin{equation}
		\boldsymbol{\hat{\beta}}_{OLS}=\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}\boldsymbol{X}'\boldsymbol{Y}\label{betaOLS}
	\end{equation}
	with variance matrix
	\begin{equation}
		\operatorname{Var}(\hat{\boldsymbol{\beta}}_{OLS})=\sigma_Y^2\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}. \label{eq:varOLS}
	\end{equation}
	 In fact it is the Best Linear Unbiased Estimator (BLUE).
	 The theoretical \textsc{mse} is given by
	\begin{equation}
	\textsc{mse}(\hat{\boldsymbol{\beta}}_{OLS})= \sigma_Y^2 \operatorname{Tr}((\boldsymbol{X}'\boldsymbol{X})^{-1}). \nonumber 
	\end{equation}
		\end{frame}

\begin{frame}{Running example}

@@

		\begin{frame}{ SEM }
		 Modélisation de la structure mais à la main et aucun impact sur l'estimation
		 \end{frame}

		\begin{frame}{ Selvarclust }
			Semble très bien mais n'aboutit pas vers la régression donc on le prolonge en CorReg
\section{Proposed Models}
	\begin{frame}{Hypothesis 1}
	There are $d_{r}\geq 0$ ``sub-regressions'', each sub-regression $j=1,\ldots,d_{r}$ having the covariate $\boldsymbol{X}^{J_{r}^j}$ as {\it response} variable ($J_{r}^j\in\{1,\ldots,p\}$ and $J_{r}^j\neq J_{r}^{j'}$ if $j\neq j'$) and having the $d_p^j>0$ covariates $\boldsymbol{X}^{J_{p}^j}$  as {\it predictor} variables ($J_{p}^j\subset\{1,\ldots,d\} \backslash J_{r}^j$ and $d_p^j=|J_{p}^j|$ the cardinal of $J_{p}^j$):
\boldsymbol{X}^{J_{r}^j}%|\boldsymbol{X}^{J_{p}^j};\boldsymbol{\alpha}_j,\sigma^2_j
=\boldsymbol{X}^{J_{p}^j}\boldsymbol{\alpha}_j+\boldsymbol{\varepsilon}_j, \label{eq:SR}
where $\boldsymbol{\alpha}_j\in{\mathbb{R}^{d_r^j}}$ (${\alpha}_j^h\neq 0$ for all $j=1,\ldots,d_r$ and $h=1,\ldots,d_p^j$) and $\boldsymbol{\varepsilon}_j \sim\mathcal{N}_n(\boldsymbol{0},\sigma^2_j\boldsymbol{I})$.
	\begin{frame}{Hypothesis 2}
	the response covariates and the predictor covariates are totally disjoint: for any sub-regression $j=1,\ldots,d_{r}$, $J_{p}^j\subset J_f$ where $J_{r}=\{J_{r}^1,\ldots,J_{r}^{d_r}\}$ is set of all response covariates and $J_f=\{1,\ldots,d\} \backslash J_{r}$ is the set of all {\it non} response covariates of cardinal $d_f=d-d_r=|J_f|$. We call this hypothesis the \underline{uncrossing rule}. Then:
			\boldsymbol{Y} %{|\boldsymbol{X},\boldsymbol{S}};\boldsymbol{\beta},\sigma_Y^2
			=\boldsymbol{X}_f\boldsymbol{\beta}_f+\boldsymbol{X}_r\boldsymbol{\beta}_r+\boldsymbol{\varepsilon}_Y. \label{eq:MainR}

@@

		\begin{frame}{Marginal properties}
		biased
		\end{frame}
		\begin{frame}{Plug-in properties}
		asymptotically unbiased
		\end{frame}
		\begin{frame}
		\begin{figure}[h!]
\centering
	\includegraphics[width=280px]{figures/MQE_toutOLSp5col.png}
	\caption{\textsc{mse} on $\hat{\boldsymbol{\beta}}$ of \textsc{ols} (plain red) and {\tt CorReg} marginal (blue dashed) and {\tt CorReg} plug-in (green dotted) estimators for varying $R^2$ of the sub-regression, $n$ and $\sigma_Y$. Results obtained on the running example with $d=5$ covariates.}\label{MQE2}
\end{figure}
		\end{frame}

\begin{frame}{Lasso Consistency}
Consistency issues of the {\sc lasso} are well known and Zhao \cite{Zhao2006MSC} gives a very simple example to illustrate it.
		We have taken the same example to show how our method is better to find the true relevant covariates.
		Here $d=3$ and $n=1\;000$.\\
		We define $\boldsymbol{X}^1,\boldsymbol{X}^2, \boldsymbol{\varepsilon}_Y, \boldsymbol{\varepsilon}_{1} \quad i.i.d. \sim \mathcal{N}(\boldsymbol{0},\boldsymbol{I}_n)$ and then \\
		\begin{eqnarray}
		\boldsymbol{X}^3%|\boldsymbol{X}^1,\boldsymbol{X}^2,\boldsymbol{S};\sigma_1^2
		&=&\frac{2}{3}\boldsymbol{X}^1+\frac{2}{3}\boldsymbol{X}^2+\frac{1}{3}\boldsymbol{\varepsilon}_1 \textrm{ and}  \nonumber \\
		\boldsymbol{Y}%|\boldsymbol{X}^1,\boldsymbol{X}^2,\boldsymbol{S};\sigma_Y^2
		&=&2\boldsymbol{X}^1+3\boldsymbol{X}^2+\boldsymbol{\varepsilon}_Y. \nonumber 
		\end{eqnarray}
\end{frame}		
	\begin{frame}{Lasso Consistency}
True $\boldsymbol{S}$ was found $991$ times on $1\;000$ tries.% (model is not identifiable because $\boldsymbol{X}^j$ are all Gaussian).
		\begin{table}[h!]
		\resizebox{\linewidth}{!}{%
		 \begin{tabular}{|c|c|c|c|}
		\hline 
		 & Classical {\sc lasso} & {\tt CorReg} marginal + {\sc lasso}& {\tt CorReg} full plug-in + {\sc lasso}\\ 
		\hline 
		True $\boldsymbol{S}$ &  1.003303 (0.046) & \textbf{1.002273} (0.046)& \textbf{1.002812} (0.046)\\ 
		\hline 
		$\hat{\boldsymbol{S}}$ & 1.003303 (0.046)& 1.017622 (0.17)& \textbf{1.002812} (0.046)\\ 
		\hline 
		\end{tabular} 
		}
		\caption{\textsc{mse} observed on a validation sample (1 000 individuals) and their standard deviation (between brackets).}\label{MSEconsistlasso}
		\end{table}

We look at the consistency  that is the real stake:
		\begin{table}[h!]	
		\resizebox{\linewidth}{!}{%
		\begin{tabular}{|c|c|c|c|}
		\hline 
		 & Classical {\sc lasso} & {\tt CorReg}  marginal + {\sc lasso}& {\tt CorReg}  full plug-in  + {\sc lasso} \\ 
		\hline 
		True $\boldsymbol{S}$ &  0 & \textbf{1000} & \textbf{835} \\ 
		\hline 
		$\hat{\boldsymbol{S}}$ & 0 & \textbf{991} & \textbf{829} \\ 
		\hline 
		\end{tabular} 
		}
		\caption{Number of consistent models found on $1\;000$ tries.}\label{testidentifiableG}
		\end{table}	
\end{frame}

\section{Structure estimation}
	\begin{frame}{•}

@@

\section{Results}
	\subsection{Simulation results}
		\begin{frame}{•}

		\end{frame}
	\subsection{Industrial results}
		\begin{frame}{•}

		\end{frame}
\section{Missing values}
	\begin{frame}{•}
	Modèle génératif complet avec dépendances
	\end{frame}
	\begin{frame}{•}
	Explosion des mélanges 
	\end{frame}
	\begin{frame}{•}
	SEM avec Gibbs 
	\end{frame}
	\begin{frame}{•}
	Bic pondéré 
	\end{frame}
	\begin{frame}{•}
	Résultats pourris 
	\end{frame}
\section{Tools}
	\begin{frame}{•}
		Excel, fonctions graphiques, arbres de décision
	\end{frame}

\begin{frame}
\bibliographystyle{apalike}
%\bibliographystyle{plain}
%\nocite{*}
\bibliography{biblio}
\end{frame}

\end{document}

>>>>

\section{Context}
	\subsection{Industrial context}
		\begin{frame}
				  \begin{enumerate}
				\item Steel industry databases.
				\item Goal: To understand and prevent quality problems on finished product, knowing the whole process, \underline{without a priori}.
			\end{enumerate}
	        \begin{center}
	          \begin{tabular}{ccc}
	         \includegraphics[width=70px,height=70px]{liquid.jpg} & \includegraphics[width=70px,height=70px]{Brame1.jpg} & \includegraphics[width=70px,height=70px]{Brame.jpg} \\
	          	\includegraphics[width=70px,height=70px]{ecras_moy.jpg} & \includegraphics[width=70px,height=70px]{tcc2.jpg} & \includegraphics[width=70px,height=70px]{bobines.jpg}
	          \end{tabular}
	        \end{center}
		\end{frame}
	\subsection{Statistical context}
		\begin{frame}{Linear Regression}
			\begin{equation}
				\boldsymbol{Y}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}\label{regressionsimple}
			\end{equation}
			where 	$\boldsymbol{\varepsilon}\sim \mathcal{N}(0,\sigma_Y^2\boldsymbol{I}_n)$	
		\end{frame}

		\begin{frame}{MLE}
		$\boldsymbol{\beta}$ can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{ols}), that is the unbiased maximum likelihood estimator \cite{saporta2006probabilites,dodge2004analyse}: %As shown in section \ref{sectionOLS}, 
	\begin{equation}
		\boldsymbol{\hat{\beta}}_{OLS}=\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}\boldsymbol{X}'\boldsymbol{Y}\label{betaOLS}
	\end{equation}
	with variance matrix
	\begin{equation}
		\operatorname{Var}(\hat{\boldsymbol{\beta}}_{OLS})=\sigma_Y^2\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}. \label{eq:varOLS}
	\end{equation}
	 In fact it is the Best Linear Unbiased Estimator (BLUE).
	 The theoretical \textsc{mse} is given by
	\begin{equation}
	\textsc{mse}(\hat{\boldsymbol{\beta}}_{OLS})= \sigma_Y^2 \operatorname{Tr}((\boldsymbol{X}'\boldsymbol{X})^{-1}). \nonumber 
	\end{equation}
		\end{frame}
		\begin{frame}{OLS}
		\begin{figure}[h!]
	\centering
	\includegraphics[width=220px]{figures/OLS_geometric_interpretation.png}
	\caption{Multiple linear regression with Ordinary Least Squares seen as a projection on the $d-$dimensional hyperplane spanned by the regressors $\boldsymbol{X}$. Public domain image.} \label{geomOLS}
	\end{figure}
		\end{frame}
\begin{frame}{Running example}

@@

		\begin{frame}{Simultaneous Equation Modeling }
		 \begin{eqnarray}
		 	\boldsymbol{X}_{n,d}&=&\boldsymbol{X}_{n,d}\boldsymbol{\beta}_{d,d} + \boldsymbol{\varepsilon}_{n,d} \nonumber
		 \end{eqnarray}
		 No real "response variable", no real estimators for recursive {\sc sem}, no real variable selection (structure finder)
		 \end{frame}

		\begin{frame}{ {\tt Selvarclust} }
			\begin{equation}
	\boldsymbol{X}^{U}%|\boldsymbol{X}^{R};\boldsymbol{\alpha},\boldsymbol{\Omega}
	=a+\boldsymbol{X}^R \boldsymbol{\alpha}+ \boldsymbol{\varepsilon}  \nonumber 
\end{equation}
	\begin{itemize}
	\item Structure based on stepwise \cite{raftery2006variable,miller2002subset}
	\item Made only for clustering purpose.
\end{itemize}

		\end{frame}
\section{Proposed Models}
	\begin{frame}{Hypothesis 1}
	There are $d_{r}\geq 0$ ``sub-regressions'', each sub-regression $j=1,\ldots,d_{r}$ having the covariate $\boldsymbol{X}^{J_{r}^j}$ as {\it response} variable ($J_{r}^j\in\{1,\ldots,p\}$ and $J_{r}^j\neq J_{r}^{j'}$ if $j\neq j'$) and having the $d_p^j>0$ covariates $\boldsymbol{X}^{J_{p}^j}$  as {\it predictor} variables ($J_{p}^j\subset\{1,\ldots,d\} \backslash J_{r}^j$ and $d_p^j=|J_{p}^j|$ the cardinal of $J_{p}^j$):
\begin{equation}
\boldsymbol{X}^{J_{r}^j}%|\boldsymbol{X}^{J_{p}^j};\boldsymbol{\alpha}_j,\sigma^2_j
=\boldsymbol{X}^{J_{p}^j}\boldsymbol{\alpha}_j+\boldsymbol{\varepsilon}_j, \label{eq:SR}
\end{equation}
where $\boldsymbol{\alpha}_j\in{\mathbb{R}^{d_r^j}}$ (${\alpha}_j^h\neq 0$ for all $j=1,\ldots,d_r$ and $h=1,\ldots,d_p^j$) and $\boldsymbol{\varepsilon}_j \sim\mathcal{N}_n(\boldsymbol{0},\sigma^2_j\boldsymbol{I})$.
	\end{frame}
	\begin{frame}{Hypothesis 2}
	The response covariates and the predictor covariates are totally disjoint: for any sub-regression $j=1,\ldots,d_{r}$, $J_{p}^j\subset J_f$ where $J_{r}=\{J_{r}^1,\ldots,J_{r}^{d_r}\}$ is set of all response covariates and $J_f=\{1,\ldots,d\} \backslash J_{r}$ is the set of all {\it non} response covariates of cardinal $d_f=d-d_r=|J_f|$. We call this hypothesis the \underline{uncrossing rule}. Then:
	\begin{equation}
			\boldsymbol{Y} %{|\boldsymbol{X},\boldsymbol{S}};\boldsymbol{\beta},\sigma_Y^2
			=\boldsymbol{X}_f\boldsymbol{\beta}_f+\boldsymbol{X}_r\boldsymbol{\beta}_r+\boldsymbol{\varepsilon}_Y. \label{eq:MainR}
\end{equation}
	\end{frame}

@@

		\begin{frame}{Marginal model's properties}
				\begin{equation}
			\mathbb{E}(\hat{\boldsymbol{\beta}}_{f}^*)=\boldsymbol{\beta}_{f}+\sum_{j =1}^{d_r}\beta_{J_r^j}\boldsymbol{\alpha}_j^* \textrm{ and }\mathbb{E}(\hat{\boldsymbol{\beta}}_{r}^*)=\boldsymbol{0}  \nonumber 
		\end{equation}

		\begin{equation}
			\operatorname{Var}(\hat{\boldsymbol{\beta}}_f^*)= (\sigma^2_Y+\sum_{j =1}^{d_r}\sigma^2_{j}\beta_{J_r^j}^2)(\boldsymbol{X}_f' \boldsymbol{X}_f)^{-1} \quad \textrm{and} \quad\operatorname{Var}(\hat{\boldsymbol{\beta}}_r^*)= \boldsymbol{0}. \label{eq:varOLS*}
		\end{equation}
		\end{frame}

\begin{frame}{Plug-in model's properties}
		Asymptotically unbiased (consistent estimators + continuous mapping theorem)
\begin{eqnarray}
	\operatorname{Var}(\hat{\boldsymbol{\beta}}_r^{\varepsilon})
	&=& \sigma^2_Y\big[\hat{\boldsymbol{\varepsilon}}'\hat{\boldsymbol{\varepsilon}}[\hat{\boldsymbol{\varepsilon}}'(\boldsymbol{I}_n-\boldsymbol{H}_f)\hat{\boldsymbol{\varepsilon}}]^{-1}\hat{\boldsymbol{\varepsilon}}'\hat{\boldsymbol{\varepsilon}}\big]^{-1} \nonumber \\
	&=&\sigma^2_Y\big[(\boldsymbol{X}_r^{\varepsilon})'\boldsymbol{X}_r^{\varepsilon}\big]^{-1}
\nonumber
\end{eqnarray}

\begin{eqnarray}
		\operatorname{Var}(\hat{\boldsymbol{\beta}}_f^{\varepsilon})
		&=&\sigma_Y^2\big[(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}+\hat{\boldsymbol{\alpha}}^*\big[(\boldsymbol{X}_r^{\varepsilon})'\boldsymbol{X}_r^{\varepsilon}\big]^{-1}(\hat{\boldsymbol{\alpha}}^*)'\big].\nonumber \label{varpluginf}
	\end{eqnarray}

@@

\begin{frame}
	\fontsize{8}{8}\selectfont{\begin{eqnarray}
	&&\operatorname{Var}_{ols}(\hat{\boldsymbol{\beta}}_{f})= \nonumber \\ 
	&& \sigma_Y^2\big[ 
(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}+(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}\boldsymbol{X}_f'\boldsymbol{X}_r
[\boldsymbol{X}_r'\boldsymbol{X}_r-\boldsymbol{X}_r'\boldsymbol{X}_f(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}\boldsymbol{X}_f'\boldsymbol{X}_r]^{-1}
\boldsymbol{X}_r'\boldsymbol{X}_f(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}\big] , \nonumber 
%	\nonumber ,\\
%	\operatorname{Var}_{ols}(\hat{\boldsymbol{\beta}}_{r})= 
%	\nonumber .
\end{eqnarray}}
\begin{equation}
\qquad = \sigma_Y^2\big[ 
(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}+\underbrace{(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}\boldsymbol{X}_f'\boldsymbol{X}_r}_{\hat{\boldsymbol{\alpha}}^*_{ols}}
[ \boldsymbol{X}_r'(\boldsymbol{I}_n-\boldsymbol{H}_f)\boldsymbol{X}_r]^{-1}
\underbrace{\boldsymbol{X}_r'\boldsymbol{X}_f(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}}_{(\hat{\boldsymbol{\alpha}}^*_{ols})'}\big] \nonumber
\end{equation}
\begin{eqnarray}
	\operatorname{Var}_{ols}(\hat{\boldsymbol{\beta}}_{r})&=&
	\sigma_Y^2\big[ \boldsymbol{X}_r'\boldsymbol{X}_r-\boldsymbol{X}_r'\boldsymbol{X}_f(\boldsymbol{X}_f'\boldsymbol{X}_f)^{-1}\boldsymbol{X}_f'\boldsymbol{X}_r\big]^{-1} \\ \nonumber
	&=&\sigma_Y^2\big[ \boldsymbol{X}_r'(\boldsymbol{I}_n-\boldsymbol{H}_f)\boldsymbol{X}_r\big]^{-1}. \nonumber
\end{eqnarray}
\end{frame}

		\begin{frame}
		\begin{figure}[h!]
\centering
	\includegraphics[width=280px]{figures/MQE_toutOLSp5col.png}
	\caption{\textsc{mse} on $\hat{\boldsymbol{\beta}}$ of \textsc{ols} (plain red) and {\tt CorReg} marginal (blue dashed) and {\tt CorReg} plug-in (green dotted) estimators for varying $R^2$ of the sub-regression, $n$ and $\sigma_Y$. Results obtained on the running example with $d=5$ covariates.}\label{MQE2}
\end{figure}
		\end{frame}

\begin{frame}{Lasso Consistency}
Consistency issues of the {\sc lasso} are well known and Zhao \cite{Zhao2006MSC} gives a very simple example to illustrate it.
		We have taken the same example to show how our method is better to find the true relevant covariates.
		Here $d=3$ and $n=1\;000$.\\
		We define $\boldsymbol{X}^1,\boldsymbol{X}^2, \boldsymbol{\varepsilon}_Y, \boldsymbol{\varepsilon}_{1} \quad i.i.d. \sim \mathcal{N}(\boldsymbol{0},\boldsymbol{I}_n)$ and then \\
		\begin{eqnarray}
		\boldsymbol{X}^3%|\boldsymbol{X}^1,\boldsymbol{X}^2,\boldsymbol{S};\sigma_1^2
		&=&\frac{2}{3}\boldsymbol{X}^1+\frac{2}{3}\boldsymbol{X}^2+\frac{1}{3}\boldsymbol{\varepsilon}_1 \textrm{ and}  \nonumber \\
		\boldsymbol{Y}%|\boldsymbol{X}^1,\boldsymbol{X}^2,\boldsymbol{S};\sigma_Y^2
		&=&2\boldsymbol{X}^1+3\boldsymbol{X}^2+\boldsymbol{\varepsilon}_Y. \nonumber 
		\end{eqnarray}
\end{frame}		
	\begin{frame}{Lasso Consistency}
True $\boldsymbol{S}$ was found $991$ times on $1\;000$ tries.% (model is not identifiable because $\boldsymbol{X}^j$ are all Gaussian).
We look at the consistency  that is the real stake:
		\begin{table}[h!]	
		\resizebox{\linewidth}{!}{%
		\begin{tabular}{|c|c|c|c|}
		\hline 
		 & Classical {\sc lasso} & {\tt CorReg}  marginal + {\sc lasso}& {\tt CorReg}  full plug-in  + {\sc lasso} \\ 
		\hline 
		True $\boldsymbol{S}$ &  0 & \textbf{1000} & \textbf{835} \\ 
		\hline 
		$\hat{\boldsymbol{S}}$ & 0 & \textbf{991} & \textbf{829} \\ 
		\hline 
		\end{tabular} 
		}
		\caption{Number of consistent models found on $1\;000$ tries.}\label{testidentifiableG}
		\end{table}	
\end{frame}

\section{Structure estimation}
	\begin{frame}
	\fontsize{8}{8}\selectfont{
	\begin{displaymath}G=\left(	\begin{array}{ccccc}
	0 & 0 & 1 & 0 & 0 \\ 
	0 & 0 & 1 & 0 & 0 \\ 
	0 & 0 & 0 & 0 & 0 \\ 
	0 & 0 & 0 & 0 & 0 \\ 
	0 & 0 & 0 & 0 & 0
	\end{array} \right)
\end{displaymath}
}
	\begin{figure}[h!]
	\centering
	\includegraphics[width=200px]{figures/graphetoy.png} 
	\caption{The bipartite graph associated to the running example. $\boldsymbol{X}_r$ is green and $\boldsymbol{X}_f$ is blue.}
	\end{figure}
	\end{frame}

\begin{frame}{Hypothesis 4: Full generative model}

All covariates $\boldsymbol{X}^j$ with $j \in J_f$ are mutually independent and arise from the following Gaussian mixture of $K_j$ components
\begin{equation}
\forall 1\leq i \leq n, \mathbb{P}(x_{i,j}|\boldsymbol{S};\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\Sigma}_j) = \sum_{h=1}^{K_j} \pi_{j,h} \Phi(x_{i,j};\mu_{j,h} ,\Sigma_{j,h}), \nonumber
\end{equation}
where $\boldsymbol{\pi}_{j}=(\pi_{j,1},\ldots,\pi_{j,K_j})$ is the vector of mixing proportions with $\forall 1\leq h\leq k_j , \pi_{j,h}>0$ and $\sum_{h=1}^{K_j}\pi_{j,h}=1$, $\boldsymbol{\mu}_j=(\mu_{j,1},\ldots,\mu_{j,K_j})$  is the vector of centres and $\boldsymbol{\Sigma}_j=(\Sigma_{j,1},\ldots,\Sigma_{j,K_j})$ is the vector of variances and $\Phi$ is the Gaussian density function. \\We stack together all these mixture parameters in $\boldsymbol{\theta}=(\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\Sigma}_j ; j \in J_f)$. We now have a full generative model on $\boldsymbol{X}$.
\end{frame}

\begin{frame}{Penalized BIC}
we propose to introduce some information in $\mathbb{P}(\boldsymbol{S})$ promoting simple models through the following {\it hierarchical} uniform distribution denoted by $\mathbb{P}_H(\boldsymbol{S})$:
\fontsize{10}{10}\selectfont{\begin{eqnarray}
\mathbb{P}_H(\boldsymbol{S}) & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p) \nonumber \\
 & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p,d_r,\boldsymbol{d}_p)  \nonumber \\
 & = & \mathbb{P}_U(\boldsymbol{J}_p|\boldsymbol{d}_p,\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{d}_p|\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{J}_r|d_r)\times \mathbb{P}_U(d_r)  \nonumber \\
 & = & \left[\prod_{j=1}^{d_r} \left(\begin{array}{c} d-d_r \\ d_p^j \end{array}\right) \right]^{-1} \times \left[d-d_r\right]^{-d_r} \times \left[\left(\begin{array}{c} d \\ d_r \end{array} \right)\right]^{-1} \times [d+1]^{-1} \nonumber 
\end{eqnarray}
}
\end{frame}
\subsection{Markov chain}
\begin{frame}
		At each step the Markov chain moves with probability:
	\begin{eqnarray}
			\forall \boldsymbol{S} \in \mathcal{S}_d, \forall \boldsymbol{S}^+\in \mathcal{V}(\boldsymbol{S}): %\mathcal{P}_{\boldsymbol{S},\boldsymbol{S}^+}=
			\mathbb{P}(\boldsymbol{S}^+|\mathcal{V}(\boldsymbol{S}))&=&\frac{\exp{(-\mbox{{\sc bic}}_*(\boldsymbol{S}^+))}}{\sum_{\tilde{\boldsymbol{S}}\in \mathcal{V}(\boldsymbol{S})}\exp{(-\mbox{{\sc bic}}_*(\tilde{\boldsymbol{S}}))}} \nonumber
	\end{eqnarray}
	where $\mathcal{V}(\boldsymbol{S})$ is a neighbourhood and $\mathcal{S}_d$ is the set of feasible structures within $d$ variables.
\end{frame}

\begin{frame}
	For each step $(q)$, starting from $\boldsymbol{S} \in \mathcal{S}_d$ we define a neighbourhood:
		\begin{eqnarray}
		\mathcal{V}(\boldsymbol{S})&=& \{\boldsymbol{S} \}\cup \{ \boldsymbol{S}^{(i,j)} \in \mathcal{S}_d|(i,j) \in \mathcal{A}_{(q)}\} \nonumber 
	\end{eqnarray}	
	where $\mathcal{A}_{(q)}$ is a set of couples $(i,j) \in \{1,\dots,d \}^2$ with $i\neq j$ drawn at the step $(q)$ according to a strategy defined below and corresponding to the directed edge of the graph to modify (add or remove).
	And we have for  $\tilde{\boldsymbol{S}}=\boldsymbol{S}^{(i,j)}$:
	\begin{eqnarray}
		\forall (k,l)\neq (i,j), \quad	\tilde{\boldsymbol{G}}_{k,l}&=&\boldsymbol{G}_{k,l} \nonumber  \\
		\tilde{\boldsymbol{G}}_{i,j}&=&1-\boldsymbol{G}_{i,j}  \nonumber 
	\end{eqnarray}
	where $\tilde{\boldsymbol{G}}$ is the adjacency matrix associated to $\tilde{\boldsymbol{S}}$. Any strategy can be chosen for $\mathcal{A}_{(q)}$, from uniform distribution to specific heuristics.
\end{frame}
\subsection{Constraint Relaxation}
\begin{frame}
New definition of $\tilde{\boldsymbol{G}}$:
		Modification of the selected directed edge $(i,j)$ on the graph:
	\begin{eqnarray}
		\tilde{\boldsymbol{G}}_{i,j}&=&1-\boldsymbol{G}_{i,j} \textrm{ as usual and} \nonumber \\
		\forall k \neq i, l\neq j, \quad	\tilde{\boldsymbol{G}}_{k,l}&=&\boldsymbol{G}_{k,l} \nonumber 
\end{eqnarray}	
Column-wise relaxation :		
newly predictive covariate cannot be regressed anymore:
		\begin{eqnarray}
		\forall k \in \{1,\dots,d\}\setminus \{i\}, \tilde{\boldsymbol{G}}_{k,j}&=&\boldsymbol{G}_{i,j}\boldsymbol{G}_{k,j}  \nonumber  \\
				\end{eqnarray}
Row-wise relaxation: newly regressed covariate cannot be predictive anymore:
		\begin{eqnarray}
		\forall l \in \{1,\dots,d\}\setminus \{j\}, \tilde{\boldsymbol{G}}_{i,l}&=&\boldsymbol{G}_{i,j}\boldsymbol{G}_{i,l} \textrm{ (row-wise relaxation)} \nonumber 
	\end{eqnarray} 
\end{frame}
